Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-07 draft.tex
add intuition for strategy profiles and move description of eqm path actions

\textbf{Need text to give intuition or tell where I'm going to give intuition.}

@@

Thus, given Conditions (1)-(6) hold, equilibrium strategies for each period in this status quo equilibrium are:
\begin{itemize}
	\item Player $p$ spends more than $c$ is willing to invest to ensure the incentives for the status quo outcome are in place in period $t$ whenever this is affordable. That is, $p$ invests $R_{pt} = \max\left\{0,\frac{\beta}{1-\delta} -(q_{st} - l_{st})\right\}\leq B_{pt}$. If this inequality is violated, $p$ invests nothing.
	\item Player $c$ invests $R_{ct} = \frac{\beta}{1-\delta} -(Q_{st} - l_{st})$ if $\frac{\beta}{1-\delta} > (Q_{st} - l_{st})$. Otherwise, it invests nothing. 
	\item Players $s$ and $g$ play Status Quo as long as it yields the highest continuation value, and play Cede or Fight if continuation values from either exceeds the status quo continuation value. 
\end{itemize}

Equilibrium actions are for $p$ to maintain the status quo by investing $\mu$ each period once the difference in payoffs to $s$ from playing Status Quo and Cede reaches $\frac{\beta}{1-\de}$ (with a possible lump sum investment at $t=1$ of up to that amount); for $c$ to not invest and for both $g$ and $s$ to play Status Quo each period. \hfill $\blacksquare$

@@

By contributing $\mu$ in each period, the patron supplies sufficient resources to the unrecognized state to ensure that the secessionist elite prefers the status quo to surrendering independence.

>>>>

To understand this equilibrium, notice that there are three possible ways to disturb the Status Quo: (1) the international community can provoke the secessionists to Cede, (2) the patron can provoke the government to cede, or (3) the patron can provoke the secessionists to fight.\footnote{The international community might also provoke the government to fight, but it is assumed to avoid conflict.} In order for the Status Quo Equilibrium to persist, each of these three disturbances must be deterred.

Since the patron moves first, in the Status Quo Equilibrium, the only investment that takes place is the patron's investment in the status quo payoffs of the secessionists to deter the international community from provoking the secessionists to cede the issue of sovereignty. The international community's willingness to counteract investments by the patron toward the other two disturbances implies that there will be no investments in equilibrium in cases (2) and (3).

If, however, off-path investments are ever made such that Status Quo does not yield the highest continuation value for one of the players, that player will play Cede or Fight and the game will end.

Equilibrium actions are for the patron to maintain the status quo by investing $\mu$ each period once the difference in payoffs to the secessionists from playing Status Quo and Cede reaches $\frac{\beta}{1-\de}$ (with a possible lump sum investment at $t=1$ of up to that amount); for the international community to not invest and for both inside actors to play Status Quo each period.

@@

@@

By contributing $\mu$ in each period, the patron supplies sufficient resources to the unrecognized state to ensure that the secessionist elite prefers the status quo to surrendering independence.   \hfill $\blacksquare$
